\sysfull

### 2018-08-04 paper/asplos19/systemdescription.tex
revising system description

% HERE -----------------------------
\textbf{Virtual Memory Manager.} \sys is able to efficiently coalesce
tasks because of its efficient virtual memory manager. \sys's memory manager
paginates memory and ensures that data in a page remain consistent despite
power interruptions. \sys allows a task to manipulate data in a volatile copy
of a page only. Pages swap between volatile and non-volatile memory, depending
on the capacity of the volatile memory and the program's access pattern. \sys
tracks a task's memory accesses efficiently at page granularity (rather than
using, e.g., costly word-granular tracking). When a task ends, each page it
accessed commits from volatile memory (or from a non-volatile swap region for
dirty pages) back to the non-volatile main memory. Pages efficiently,
atomically commit using a two-phase commit procedure accelerated using hardware
support for direct memory access (DMA). Section~\ref{sec:memory_virtulaization}
provides details of \sys's memory manager.

>>>>

\textbf{Virtual Memory Manager.} \sys is able to efficiently coalesce
tasks because of its efficient virtual memory manager (VMM).
the VMM privatizes a group of memory pages demanded by a coalesced task, and limits an application access only to the fast volatile memory. It persists all pages modifications in non-volatile memory on a coalesced task transition. Section~\ref{sec:memory_virtulaization} provides details of VMM.
